\subsection{Axis Labelling}
Axes remain unlabelled. It would be clearer if these were labelled with text $x$, $y$, $z$, and $\mathbf{n}$, with $\mathbf{n}$ representing the director.

\subsection{Colour Palette Guide}
Currently, there is no visual guide for a molecule's colour derived from its principal axis angle with the director. While this can be seen relatively intuitively, a colour palette should be displayed somewhere in the UI which shows a mapping of colour to angles (in the range $[0, \pi)$).

\subsection{Colour Palette Adjustment}
The current palette for molecule colouring based on its principal axis' director alignment assumes a colour range with hue $0$ (red) through to $\frac{-4\pi}{3}$ (blue). A different range is easily obtained with the current current colour sampling code by simply giving a different start and end point. This could be added to the GUI to allow for specifying some custom colouring scheme if needed.

\subsection{Spherocylinder Shading}
The spherocylinder shading does not quite appear visually correct. Normal generation should be inspected to check for errors. See \cref{shape_bug_spher}.

\subsection{Variable LOD GUI Settings}
While default values are tuned to hide geometry changes, distances at which geometries are lowered in quality should somehow be changeable within the GUI.

\subsection{Periodic Repetition LOD Bug}
When molecules are repeated, the repeated molecule geometries are not replaced when the level of detail is changed. This should be addressed by fixing the update logic.

\subsection{Bug Fixes}
A thorough review of as many setting combinations as possible should be performed to identify further desynchronisation conditions between the visualisation shown and changed settings.
